### 2016-10-19 methodsPaper/tex/results.tex
Created two new figures
Also created appendix.Rnw to store old R code.

Our subset of the US population to only metropolitan counties
consisted of 1,090 of 3,141 (34.7\%) counties, or ???X??? of ???Y???
(???Z???\%) of the total US population. The age and gender
distribution of our subset population was slightly younger (???making
this up???) than the national population. Active transport times
(walking and cycling) for baseline, low, and high scenarios are shown
in \ref{fig:ATtimes}. Overall mean walking time for high and low
scenarios were ???X??? (min/week) higher and ???Y??? (min/week) lower
than baseline, respectively. Baseline non-travel activity time was
estimated to be ???X??? (min/week) from the ATUS for US metropolitan
populations.

Comparing baseline to low/high scenarios produced estimates of ???X???
change in the disease burden (1,000s DALYs) for our US population
subset. We then varied the mean non-travel activity time and active
travel time to observe how this chaged results
(\ref{fig:currentFig1}). We observe the most dramatic responses in
disease burden estimates to changes in active travel time when
non-travel activity times are lowest. This result is consistent with
the non-linear dose-response curve for physical activity and several
health outcomes. The total health benefit of increased active travel
time (high scenario) varies from ???X??? to ???Y??? with changing mean
non-travel activity time (0 to 25 minutes).

@@

As exhibited in Figure \ref{fig:percentQuint}, the variability in
disease burden benfits varies to a much greater degree when using
fewer points in the attirbutable fraction approximation.

>>>>

Our subset of the US population to only metropolitan counties
consisted of 1,090 of 3,141 (34.7\%) counties, or ???X??? of ???Y???
(???Z???\%) of the total US population. The age and gender
distribution of our subset population was slightly younger (???making
this up???) than the national population. Active transport times
(walking and cycling) for baseline, low, and high scenarios are shown
in \ref{fig2}. Overall mean walking time for high and low
scenarios were ???X??? (min/week) higher and ???Y??? (min/week) lower
than baseline, respectively. Baseline non-travel activity time was
estimated to be ???X??? (min/week) from the ATUS for US metropolitan
populations.

Comparing baseline to low/high scenarios produced estimates of ???X???
change in the disease burden (1,000s DALYs) for our US population
subset. We then varied the mean non-travel activity time and active
travel time to observe how this chaged results (\ref{fig1}). We
observe the most dramatic responses in disease burden estimates to
changes in active travel time when non-travel activity times are
lowest. This result is consistent with the non-linear dose-response
curve for physical activity and several health outcomes. The total
health benefit of increased active travel time (high scenario) varies
from ???X??? to ???Y??? with changing mean non-travel activity time (0
to 25 minutes).

@@

As exhibited in Figure \ref{fig1}, the variability in disease burden
benfits varies to a much greater degree when using fewer points in the
attirbutable fraction approximation.
